% this file is called up by thesis.tex
% content in this file will be fed into the main document

%: ----------------------- name of chapter  -------------------------
\chapter{Conclusion} % top level followed by section, subsection


%: ----------------------- paths to graphics ------------------------

% change according to folder and file names
\ifpdf
    \graphicspath{{X/figures/PNG/}{X/figures/PDF/}{X/figures/}}
\else
    \graphicspath{{X/figures/EPS/}{X/figures/}}
\fi

%: ----------------------- contents from here ------------------------

\section{Conclusion}
In concolusion, my project implement a midi player, which is able to 
either play local midi file or connect to a remote server. The midi player  
will be a sub-module of the whole HCMP Project. With the unified APIs,  
HCMP Player can be easily extend for other usage, or integrated into 
more sophiscated project. I split the whole HCMP Player into 3 parts,  
GUI, player engine and network function. The design of each feature  
is explained in detail in previous chapters. I also briefly decribe 
implementation detail for each HCMP Player's component, as supplementary,
some pseucode segment is provide to illustrate logic. At the end, complete 
HCMP Player features is listed and a successful criteria is defined to
help evaluate the project.



\section{Future Work}
This project provide a base for some potential future works. Two other 
features can be added to extend the Player's function. There is a music score display 
component for the HCMP project, with clearly defined API, the HCMP Player can 
be easily extended as a default player for music display component. 
Display with the addition of a midi score follower, 
the music display could be synchronized 
to a live keyboard performance and the Player could play an accompaniment 
part and the user can read the score from the Player's virtual keyboard. 
Dawen Liang's previous work \cite{Dawen:ISMIR2011}on music database provide 
user a convenient way to record, organize
and retrieve audio information from various sources. The Player can further integrate 
this feature to provide a powerful audio library management tool.
