% this file is called up by thesis.tex
% content in this file will be fed into the main document

%: ----------------------- name of chapter  -------------------------
\chapter{Evaluation} % top level followed by section, subsection


%: ----------------------- paths to graphics ------------------------

% change according to folder and file names
\ifpdf
    \graphicspath{{X/figures/PNG/}{X/figures/PDF/}{X/figures/}}
\else
    \graphicspath{{X/figures/EPS/}{X/figures/}}
\fi

%: ----------------------- contents from here ------------------------

\section{Overview}
Chapter 6 mainly focuses on the evaluation of the project. In
this chapter, we define the successful criteria of the project and discuss
how to meet those requirements. A complete list of required features is
listed. At the last part of the chapter, we also make a brief performance test 
and discuss some potential performance issues.

\section{Functional Evaluation}
Based on the project design from previous chapters, the evaluation of the 
project contains two parts. To be successful, the project needs to satisfy 
the functional requirements as well as all of the performance 
requirements. The functional requirement cover all the basic functions of 
the HCMP Player. Each functional requirement has been tested manually or 
automatically by scripts. As for the performance test, some code segments 
have been added to the original program to test the general performance issues.

\subsection{Stand-alone Mode Requirement}
\begin{enumerate}
  \item The user should be able to load and play normal MIDI files.
  \item The user should be able to play, pause, and stop while playing MIDI files.  
  \item The user should be able to freely adjust tempo, while playing the MIDI files.
  \item Data visualization components should correctly show the MIDI notes 
        and synchronize with the audio stream while playing the MIDI files.
  \item Each track component should match to colors on the data visualization 
        component.
  \item Each track component should be able to mute, solo and adjust volume.  
  \item The player should contain a simple MIDI library to manage MIDI files. 
        The library should automatically remember recently imported MIDI files.
  \item The player should provide a complete configuration interface for the 
        user. All of user's settings should be saved automatically.
  \item The configuration of the HCMP Player should be saved into a file.
\end{enumerate}

\subsection{Network Mode Requirement}
\begin{enumerate}
  \item Each instance of the HCMP Player runs in its own process space. One player 
        should not affect another player's function or performance. 
        
  \item Each HCMP Player should be launched separately by the user. After 
        launching, the MIDI player should automatically connect to a Conductor 
        based on its configuration.

  \item If the HCMP Player fails to establish a connection with the Conductor, 
        it should rollback to the stand-alone mode without crashing.

  \item The Conductor communicates with the MIDI player through a predefined API. 
        The API is defined in Chapter 5. After establishing a connection with 
        the Conductor, the HCMP Player should register with Conductor's 
        {\bf Dependent} list. Once a command is received, the Conductor sends 
        messages to all the HCMP Players that previously registered in the 
        {\bf Dependent} list. 

  \item Multiple instances of the HCMP Player should be able to connect to one Conductor. 
  \item After establishing a connection with the Conductor, the HCMP Player 
        should be able to receive tempo information from the Conductor and 
        synchronize with it.     
  \item The Conductor should be able to explicitly command certain HCMP players to 
        load a specified configuration file or it can directly 
        send configuration information through the network to that HCMP player.
  \item 
    The HCMP Player is compatible with Zeromq API, 
    and the 4 core functions will be
    \begin{itemize}
      \item \texttt{play} - ask a HCMP Player to start playing 
      \item \texttt{stop} - stop a HCMP Player from playing 
      \item \texttt{update time-map} - send a new time-map to the HCMP Player 
      \item \texttt{set position} - set the position to a certain beat
    \end{itemize}
\end{enumerate}

\subsection{Performance Requirement}
\begin{enumerate}
  \item The HCMP Player GUI should always respond to user input without 
        significant delay, and the GUI thread should not hang.
  \item The HCMP Player should respond to the Conductor without significant delay.
  \item The HCMP Player should use no more than 100MB of memory.
  \item The HCMP Player should use a reasonable amount of CPU resource while playing 
        MIDI files.
  \item The HCMP Player should not crash.
\end{enumerate}

\section{Test Plan}
\subsection{Functional Test}
A functional test aims to test all of the features listed above. Some of the 
key test cases are listed below.
\begin{itemize}
  \item Test case 1 -- Load 10 different MIDI files, each having a different
        length, including an invalid MIDI file.
  \item Test case 2 -- Load 10 different MIDI files, change the tempo from high to 
        low, and then from low back to high. Change the tempo every 0.5s.
  \item Test case 3 -- Load 10 different MIDI files, use the track panel to mute
        from the first track to the last track, then do a similar action with the 
        volume adjust.
  \item Test case 4 -- Load 10 different MIDI files into the HCMP Player library. 
        Click each track to import, then delete all of the files on the disk, and 
        click each track again.
  \item Test case 5 -- Create a virtual conductor and create a HCMP Player use  
        the network function to connect to the Conductor. The Conductor issues a command
        to test each network operation to make sure it works correctly. 
  \item Test case 6 -- Create a virtual conductor and create 10 HCMP Players, 
        all connected to the Conductor. The Conductor issues a command to test 
        each network operation to make sure everything work correctly.
  \item Test case 7 -- Create a virtual conductor and create a HCMP Player 
        to connect to the Conductor. While the HCMP Player is playing the 
        file, cut the
        network connection and determine if the HCMP Player behaves correctly.
  \item Test case 8 -- Create a virtual conductor and create 10 HCMP Players, observing
        if all connected to the Conductor. The Conductor explicitly asks each 
        HCMP Player to play with a certain configuration file.
\end{itemize}

\subsection{Performance Test}
The performance test aims to test the general performance of the HCMP Player. Two 
important aspects for the performance test are the Canvas redraw test and the MIDI
event test. 

As described in previous chapters, the Canvas redraws the whole bitmap every time 
the beat updates. The bitmap will be updated approximately 20 times per second.
Even though the bitmap size is relatively small, it is still possible to become 
a bottleneck for the whole system. Any inefficiency in the code will lead to GUI 
lag or it may hang there without responding to user input. Test case 1 tries 
to measure the general accumulative time spent on redrawing. 

Another issue involves MIDI events. The player engine uses a real-time scheduler to  
constantly poll and execute events. Ideally, the event is dispatched at its 
scheduled time, or at least we should control it so that events are dispatched within 
a certain limited time. Test case 2 aims to measure the overall latency between 
the ideal scheduled time and the actual invoked time. 
\subsubsection{Performance Test Case}
\begin{itemize}
  \item Test case 1 -- Measure the time between the Canvas redraw routine, and 
        add each redraw time together to obtain total time spent on drawing. 
        Calculate the ratio of the redraw time and the total time.
  \item Test case 2 -- In the player engine, after the event has been dispatched, 
        check the ideal time stored in that event, get the current time, calculate 
        the latency. Change the tempos, and measure the latency again.
\end{itemize}
